### 2019-12-14 README.Rmd
Add sz_lines
Doughnuts for breakfast
cc @mtennekes

```{r}
library(sf)
devtools::load_all()
plot(sz_study_region)
```

@@

```{r}
x = sz_study_region
q = sz_quadrat(x, 4) # break into 4
plot(q)
```

Or dohnuts

```{r}
plot(sz_dohnut(x, n = 4))
dohnut_4km = sz_dohnut(x, d = 4)
dohnut_4km
plot(sf::st_geometry(dohnut_4km))
plot(dohnut_4km[3, ], col = "blue", add = TRUE)
```

>>>>

```{r}
library(sf)
devtools::load_all()
plot(sz_region)
```

@@

```{r}
x = sz_region
q = sz_quadrat(x, 4) # break into 4
plot(q)
```

Or doughnuts

```{r}
plot(sz_doughnut(x, n = 4))
doughnut_4km = sz_doughnut(x, d = 4)
doughnut_4km
plot(sf::st_geometry(doughnut_4km))
plot(doughnut_4km[3, ], col = "blue", add = TRUE)
```
